MLCommons Earthquake Science Benchmark

### 2022-02-21 paper-capstone-earthquake.tex
add markdown

\PassOptionsToPackage{hyphens}{url}
\documentclass[sigplan,screen]{acmart}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[pdf]{graphviz}
\usepackage{xpatch}
\usepackage{adjustbox}
\usepackage{makecell} 
\usepackage{ifthen}
\usepackage{comment}

@@

\newcommand{\BIOFIG}[3]{%
\parindent 0pt%
\setlength{\intextsep}{6pt}%
\setlength{\columnsep}{6pt}%

@@

\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

@@

\TODO{Add your personal computers to this table \url{https://github.com/Data-ScienceHub/mlcommons-science/issues/37}}
\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:desktops}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|l|r|l|l|l|l|l|}
        \hline
        See also & Organization   & Machine                         & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         Table \ref{tab:gcompute}   & 
         Gregor    & 
         5950X   &  
         1 &   
         \href{https://www.gigabyte.com/Graphics-Card/GV-N307TGAMING-OC-8GD#kf}{GIGABYTE Gaming RTX 3070TI}  & 
         8GB & 
         1 & 
         1 & 
         Sep 2021   \\
            & 
            & 
            &  
            &   
         \href{https://rog.asus.com/us/graphics-cards/graphics-cards/rog-strix/rog-strix-rtx3090-o24g-gaming-model/}{ASUS ROG Strix RTX 3090} & 
         24GB & 
         1 & 
         1 & 
         Feb 2022   \\
         \hline
         \ref{sec:tcomputer}   & Thomas.A  & i7-8750H &  1 &   NVIDIA GeForce RTX 2070 with Max-Q Design  & 16GB & 1 & 1 & 2019   \\
         \hline
         \ref{sec:t2computer}   & Thomas.B  & i7-7700HQ &  1 &   NVIDIA GeForce GTX 1060  & 16GB & 1 & 1 & 2017   \\
         \hline
         Table \ref{tab:rcompute} & Rob.K & AMD Ryzen 9 5900HX & 1 &  NVidia RTX 3080 &  16GB & 1 & 1 & 11/25/2021 \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\begin{itemize}
    \item Introduction to Python \cite{las-intro-python}
\end{itemize}

@@

>>>>

\PassOptionsToPackage{hyphens}{url}
\documentclass[sigplan,screen]{acmart}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[pdf]{graphviz}
\usepackage{xpatch}
\usepackage{adjustbox}
\usepackage{makecell} 
\usepackage{ifthen}
% \usepackage[smartEllipses]{markdown}
\usepackage{comment}

@@

\newcommand*\rot{\rotatebox{90}}
\newcommand{\BIOFIG}[3]{%
\parindent 0pt%
\setlength{\intextsep}{6pt}%
\setlength{\columnsep}{6pt}%

@@

\begin{CCSXML}
<mdcs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

@@

\TODO{Add your personal computers to this table \url{https://github.com/Data-ScienceHub/mlcommons-science/issues/37}}
\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:desktops}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|l|l|r|r|r|l|r|l|l|l|}
        \hline
        See also & 
        Organization   & 
        Machine                         &
        OS & 
        \rot{Processors~} &
        \rot{Core~} & 
        \rot{Threads~} & 
        GPUs             & 
        \rot{\makecell{Memory\\/Device}} &  
        \rot{GPU/Device} & 
        \rot{No. of nodes~} & 
        Commissioned \\ 
        \hline
        \hline
         Table \ref{tab:gcompute}   & 
         Gregor    & 
         5950X   &  
         Ubuntu 20.04&
         1 &   
         16 & 
         32 &
         \href{https://www.gigabyte.com/Graphics-Card/GV-N307TGAMING-OC-8GD#kf}{GIGABYTE Gaming RTX 3070TI}  & 
         8GB & 
         2 &
         1 &
         Sep 2021   \\
            & 
            &
            &
            &
            & 
            &  
            &   
         \href{https://rog.asus.com/us/graphics-cards/graphics-cards/rog-strix/rog-strix-rtx3090-o24g-gaming-model/}{ASUS ROG Strix RTX 3090} & 
         24GB & 
         & 
         & 
         Feb 2022   \\
         \hline
         \ref{sec:tcomputer}   & Thomas.A  & i7-8750H & Win11 Pro  & 1 &   ? & ? & NVIDIA GeForce RTX 2070 with Max-Q Design  & 16GB & 1 & 1 & 2019   \\
         \hline
         \ref{sec:t2computer}   & Thomas.B  & i7-7700HQ &  Win11 Pro &1 & ? & ? &  NVIDIA GeForce GTX 1060  & 16GB & 1 & 1 & 2017   \\
         \hline
         Table \ref{tab:rcompute} & 
         Rob & 
         5900HX & 
         Win11 Pro & 
         1 & 
         8 & 
         16 & 
         NVIDIA RTX 3080 &  
         16GB & 
         1 & 
         1 & 
         11/25/2021 \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\begin{itemize}
    \item Introduction to Python \cite{las-intro-python}, Gregor von Laszewski, with contributions from Robert Knuuti
    \item \href{https://laszewsk.github.io/mlcommons/docs/tutorials/rivanna/}{Running GPU Batch jobs on Rivanna} Gregor von Laszewski, Robert Knuuti
\end{itemize}

@@

% \markdownInput{rivanna-manual}
